---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ehsr [under development]

<!-- badges: start -->
<!-- badges: end -->

A work-in-progress R package to facilitate the importation of English Housing Survey (EHS) data files that you have already downloaded from the UK Data Service. When pointed to a folder where the EHS files are saved, `ehsr` can identify and import the files for a given year or series of years, join them together into a single object, standardise variable names and convert labelled values to factors.

Your use of data downloaded from the UK Data Service must  be consistent with the requirements and conditions of the UKDS that you agreed to when accessing the data.

## Installation

You can install the development version of `ehsr` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("jgleeson/ehsr")
```

Or

```r
# install.packages("devtools")
devtools::install_github("jgleeson/ehsr")
```

## Example

`ehsr` currently contains four functions, which import just the 'derived' EHS household datasets, a defined set of variables from the detailed household datasets, a list of households that contain concealed households or a defined set from the detailed housing stock datasets. 

If you have already downloaded the EHS special licence data for 2022 and have assigned the path where your EHS datasets are saved to the 'folder' object, the first function is used as follows.

```{r assign folder, include= FALSE}
folder <- ("~/Library/CloudStorage/OneDrive-SharedLibraries-GreaterLondonAuthority/HL_HOU_Policy - Documents/Analysis team/Survey data/EHS/")
```
```{r example}
library(ehsr)

d <- hh_derived(folder, 2022)
```
